---
title: "CSVM Logbook"
author: "Marc Groefsema"
date: \today
output: pdf_document
---

\section{Influence of second order Soft Assignment}
I'd like to know what the influence of 'second order soft assignment' is, compared to regular Soft Assignment
patchSize = 12, stride = 2.
As feat. descriptor, HOG is used, with 4x4 cells.
As codebook, a deep convolutional codebook is used.

The settings will be tested on the MNIST dataset, with 6000 random images to train, and 1000 images to test.
As a classifier the CSVM will be used, with learningRate = 0.000002, and 20000 iterations, wieghtInit = 0.002, C = 1000

These settings are not proven to be the "best" settings for each, both the provide a common context for this experiment, with only the type of assignment function as controlled variable.

Here hog uses no padding

With both settings, 8 runs are done.
To compare the two codebook activation function, a two-sides paired t-test is used.
A P-value threshold of 0.05 will be used.

```{r}
SoftAssignment <- c(87.2, 86.6, 87.7, 88.2, 85.9, 86.0, 84.2, 86.5)
SoftAssignmentClipping <- c(87.6, 84.7, 83.6, 84.5, 84.1, 83.0, 85.8, 85.5)

t.test(SoftAssignment, SoftAssignmentClipping, paired = FALSE, alternative = "two.sided")

```

This test shows that in second order soft assignment performs slightly worse than a first order soft assignment.

\section{Influence of the amount of centroids used}
I'd like to explore the influence of the number of centroids used in MNIST on the classification rate.
All values are gained from a 8 fold crossvalidation. The same settings as the above experiment are used, with normal Soft Assignment and a Deep Codebook.

Here HOG uses identity padding

```{r}
v10centr <- c(66.4, 75.0, 63.5, 75.5, 75.3, 78.2, 73.2, 72.7)
v30centr <- c(83.4, 86.0, 85.5, 85.5, 83.7, 83.9, 84.8, 83.4)
v50centr <- c(87.2, 86.1, 87.8, 88.5, 88.5, 85.5, 88.0, 87.4)
v70centr <- c(88.2, 89.3, 89.9, 89.9, 88.5, 89.3, 88.1, 88.3)
v90centr <- c(89.9, 90.0, 89.7, 88.3, 89.5, 91.2, 87.8, 88.7)
v110centr <- c(90.0, 90.6, 91.5, 91.8)
v130centr <- c(1)
```


\section{}
